\chapter{Background}
\label{chapter:Background}
This chapter summarizes the necessary theoretical an technological background topics of the thesis.

\section{Axioms of Linguistic Architectures}
\label{section:AxiomsOfLinguisticArchitectures}
This section summarizes axioms of linguistics architectures.
\ToDo{explaing 'lingustic architectures' with terms such as vocabulary, ...}
Axioms of linguistic architectures are outlined in \cite{DBLP:conf/sle/Lammel16} and refined in \cite{HeinzLV17}.
ยง\ref{subsection:Parthood} 

Axioms are presented as First Order Logic and formalization is taken from \cite{HeinzLV17}.
The universe to draw elements from is represented by the \Entity-predicate:
\begin{align*}
\forall x.\Entity(x).
\end{align*}
We assume it holds for everything of interest, hence such things are called \textit{entities}.

Linguistic architectures intend to describe software from language centric point of view, thus we provide specializations of entities for languages:
\begin{align*}
&\Set(x) \Rightarrow \Entity(x).\\
&\Language(x) \Rightarrow \Set(x).
\end{align*}
There are entities representing sets in a mathematical sense, and there are sets representing (formal-) languages in the sense of theoretical computer science.

On the other hand, we provide specializations for entities involved in software engineering terminology:
\begin{align*}
&\Artifact(x) \Rightarrow \Entity(x).\\
&\File(x) \Rightarrow \Artifact(x).\\
&\Folder(x) \Rightarrow \Artifact(x).
\end{align*}
There are entities representing all kinds of digital artifacts, e.g. files and folders.
Files represent persistent data resources, locatable either trough file systems or web services.
Folders represent locatable collections of files.
The intended use and semantic of these predicates is not meant to differ from intuitive, every day use.


\subsection{Parthood}
\label{subsection:Parthood}
\Gls{Parthood} is an essential relationship when reasoning about \gls{Correspondence} and \gls{Conformance} among artifacts within linguistic architectures \cite{DBLP:conf/sle/Lammel16} \cite{HeinzLV17}.
It describes the relation between entities and their constituent parts.
The study of \gls{Parthood} and its derivatives is \gls{Mereology} \cite{DBLP:journals/dke/Varzi96} \cite{SEP:Mereology}.
In the context of linguistic architectures we assume most entities to be
composed of several conceptual or physical parts.
In short, such entities are the sum of its parts.
That is, programs may compiled from many files, systems consists of several disjoint but dependent components, a \gls{Java} class is made up of methods and fields, etc.
Furthermore such entities are considered to be \textit{mereologically invariant}, i.e. if one part changes, the whole changes as well. 
Axiom \ref{axiom:PartOf} captures \gls{Parthood} at its most basic level.
\begin{axiom}[\partOf]
\label{axiom:PartOf}
\begin{align*}
&\partOf(p,w)
\Rightarrow
\Entity(p) \wedge \Entity(w).\\
&\partOf(p,w)
\Leftarrow
p \text{ is a constituent part of } w.
\end{align*}
\end{axiom}
\Gls{Parthood} is usually considered to be reflexive, antisymmetric and transitive \cite{DBLP:journals/dke/Varzi96} \cite{SEP:Mereology}, thus facilitating a partial order:
\begin{align*}
&\partOf(p,p). &\text{Reflxivity}\\
&\partOf(p,w) \wedge \partOf(w,p)
\Rightarrow
p = w. &\text{Antisymmertry}\\
&\partOf(p,w) \wedge \partOf(w,u)
\Rightarrow 
\partOf(p,u). &\text{Transitivity}
\end{align*}
The irreflexive \gls{Parthood} relationship is called proper:
\begin{align*}
&\properPartOf(p,w)
\Rightarrow
\Entity(p) \wedge \Entity(w).\\
&\properPartOf(x,y)
\Leftarrow
\partOf(x,y) \wedge \neg \partOf(y,x).
\end{align*}
Proper \gls{Parthood} is the strict order induced by normal \gls{Parthood}.
Figure \ref{figure:SchematicProperPart} shows a schematic illustration of proper parts.
\begin{figure}[h!]
\begin{center}
\begin{tikzpicture}[scale=0.8]
\draw[draw=black,thick](0,0)circle(2 and 2);
\draw[fill=gray!10,draw=black,thick](-0.5,0)circle(1 and 1);
\draw(-0.5,0)node{\textbf{x}};
\draw(1,0)node{\textbf{y}};
\node[anchor=north] at (current bounding box.south) {$\properPartOf(x,y)$};
\end{tikzpicture}
\end{center}
\caption{A schematic depiction of Proper Parthood}
\label{figure:SchematicProperPart}
\end{figure}
This Venn-style diagram depicts the scenario where $x$ is certainly a part of $y$, however $y$ is not a part of $x$.
In general proper \gls{Parthood} is a asymmetric relationship:
\begin{align*}
&\properPartOf(x,y) 
\Rightarrow
\neg \properPartOf(y,x).
&\text{Asymmetry}
\end{align*}

\Gls{Mereology} also allows for the notion of atomicity \cite{DBLP:journals/dke/Varzi96} \cite{SEP:Mereology}, i.e. atomic parts which cannot be decomposed in further parts:
\begin{align*}
\atomicPart(x)
\Leftarrow
\not \exists p.\partOf(p,x).
\end{align*}
Atomicity is later used to distinguish cases for \gls{Correspondence} and \gls{Conformance} (see ยง\ref{subsection:Correspondence} and ยง\ref{subsection:Conformance}).

\subsection{Fragments}
\label{subsection:Fragments}
\Glspl{Fragment} are a specialization of entities intended to capture the endogenous, mereological decomposition of artifacts \cite{HeinzLV17}.
Axiom \ref{axiom:Fragment} defines  \glspl{Fragment} as artifacts, which are neither files nor folders, and are properly embedded in at least one other artifact.
For instance, consider the syntactical decomposition of \gls{Java} classes, i.e. the class \gls{Fragment} contains method and field \glspl{Fragment}.
\begin{axiom}[\Fragment]
\label{axiom:Fragment}
\begin{align*}
&\Fragment(f) 
\Rightarrow
\Artifact(a) \wedge \neg(\File(f) \vee \Folder(f)).\\
&\Fragment(f) 
\Rightarrow 
\exists a.\Artifact(a) \wedge \properPartOf(f,a).
\end{align*}
\end{axiom}
We emphasize the proper \gls{Parthood} here, since not all authors necessarily consider \partOf~ to be reflexive \cite{DBLP:conf/sle/Lammel16} \cite{HeinzLV17}.
However, we previously distinguished between reflexive and irreflexive \gls{Parthood} and if we were to use reflexive \gls{Parthood} for the definition of the \Fragment-predicate it would be a tautology:
\begin{align*}
&\Fragment(f) 
\Rightarrow 
\exists a.\Artifact(a) \wedge \partOf(f,a).
&\text{Tautology}
\end{align*}
Since $\Fragment(f)$ implies $\Artifact(f)$ and \partOf~ is reflexive there is always an artifact for a \gls{Fragment} the latter is a part of, that is the \gls{Fragment} itself.

From the specification of \glspl{Fragment} we can first specialize the proper \gls{Parthood} predicate:
\begin{align*}
&\fragmentOf(f,x) 
\Rightarrow
\Fragment(f) \wedge \Artifact(x).\\
&\fragmentOf(f,x) 
\Leftarrow
\Fragment(f) \wedge \Artifact(x) \wedge \properPartOf(f,x).
\end{align*}
This is just a restriction of domain and range facilitating a special semantic.
Secondly, we can describe the process of fragmentation:
\begin{align*}
\partOf(p,w) \wedge \Fragment(w)
\Rightarrow
\Fragment(p).
\end{align*}
The \gls{Fragment} nature propagates top-down alongside the order of \gls{Parthood}, i.e. if an entity is a \gls{Fragment} all parts are also \glspl{Fragment} \cite{HeinzLV17}.

\subsection{Correspondence}
\label{subsection:Correspondence}
\Gls{Correspondence} 

\begin{align*}
&\represents(r,e)
\Rightarrow
\Artifact(r) \wedge \Entity(e).\\
&\represents(r,e)
\Leftarrow
r \text{ is a representation of } e.
\end{align*}

\begin{align*}
&\sameAs(x,y)
\Rightarrow
\Artifact(x) \wedge \Artifact(y).\\
&\sameAs(x,y)
\Leftarrow
\exists e.\Entity(e) \wedge \represents(x,e) \wedge \represents(y,e).
\end{align*}

\begin{axiom}[\correspondsTo]
~
\newline
\resizebox{\linewidth}{!}{
\begin{minipage}{\linewidth}
\begin{align*}
\correspondsTo(x,y)
&\Rightarrow
\Artifact(x) \wedge \Artifact(y).\\
\correspondsTo(x,y)
&\Leftarrow
(\forall px.\partOf(px,x) \Rightarrow \exists py.\partOf(py,y) \wedge \correspondsTo(px,py))\\
&\wedge
(\forall py.\partOf(py,y) \Rightarrow \exists px.\partOf(px,x) \wedge \correspondsTo(py,px))\\
&\vee
(\not\exists p.\partOf(p,x) \vee \textsf{partof}(p,y)) \wedge \sameAs(x,y).
\end{align*}
\end{minipage}
}
\end{axiom}


\subsection{Conformance}
\label{subsection:Conformance}

\begin{axiom}[\conformsTo]
\begin{align*}
\conformsTo(a,d)
&\Rightarrow
\Artifact(a) \wedge \Artifact(d).\\
\conformsTo(a,a')
&\Leftarrow
(\forall p.\partOf(p,a) \wedge \exists p'.\partOf(p',a') \wedge \conformsTo(p,p'))\\
&\vee \exists t.\defines(a',t) \wedge \elementOf(a,t).
\end{align*}
\end{axiom}


\section{Traceability}
\cite{DBLP:books/daglib/p/GotelCHZEGDAMM12}

\begin{definition}[Trace]
content...
\end{definition}

\begin{definition}[Trace Link]
content...
\end{definition}


\begin{definition}[Traceability Recovery]
content...
\end{definition}


\section{Megamodeling}
\cite{DBLP:conf/sattose/BaggeZ14}
\cite{DBLP:journals/entcs/FavreN05}

\subsection{\megal}
\cite{DBLP:conf/ecmdafa/LammelV14}
\cite{DBLP:conf/models/FavreLV12}
\cite{DBLP:conf/sle/Lammel16}

\subsection{\megalxtext}
\cite{LukasHaertelBScThesis}



\section{Technical Background}

\subsection{Java Architecture for XML Binding (JAXB)}

\subsection{Hibernate}

\subsection{Another Tool For Language Recognition (ANTLR)}
\cite{Parr:2013:DAR:2501720}

